\documentclass{dm}

\usepackage{csquotes}

\newcommand{\theversion}{v0.0.0}
\title{DM Notes: Nov 11, 2017}

\begin{document}
  \begin{cols}

  \killsectionspace{}
  \section{Adventure}
    The player' travel companion died of a mysterious disease.
    They will be approached by \textbf{Remallia} and \textbf{Syndra Silvane} to find the cause by interrogating the lich, \textbf{Zaldra}.

  \begin{content}[Adventure Hook]
    Somber is the mood as the four of you stand and gaze upon the closed sarcophagus.
    On the sarcophagus is an upright gauntlet with an open eye on the back of the hand.

    A religious figure stands over the sarcophagus and says: 
    \begin{displayquote}
      Her time serving Helm in this life is over.
      But, this is not the end.
      Seanna is in good company.
      Many have died these past 11 days and they have a new purpose now.
      Take Comfort!
      She will serve Helm in the after life just like she served helm in this life
    \end{displayquote}

    The religious figure stepped back and immediately began walking away.
    A bald-headed man in long robes stepped out from a cluster of men in bright-white armor and spoke.
    \begin{displayquote}
      Please forgive \textbf{Father Avery}, he has many more burials to attend today.
      In two hours the fun will set and Seanna will be moved into \textbf{The Crypt of Helm}.
      Until them, you are welcome to stay.
    \end{displayquote}
  \end{content}

  \subsection{Remallia}
    \textbf{Remallia} is a high-level \textbf{Harper} who is looking for help in find the cause and eventually stopping \textbf{The Death Curse}.

  \subsection{Syndra Silvane}
    \textbf{Syndra} was an adventure who struck it rich, but retired after she was killed and brought back to life.

  \subsection{Journey}
    \textbf{Callbrax} (male lightfoot halfing), is the captain of the \textbf{Diviner}.
    He will take the players up the \textbf{Dessarin River} for 3 days to the Clockwood to \textbf{Zaldra's} tower.

  \subsection{Treasure}
    \textbf{Zaldra's} phylactery is in a chest with 3 spell scrolls.
    Select or roll from this table depending on the parties needs.
    Alternatively, use any level 1 wizard spells
    \begin{tabularz}
      \begin{tabularx}{\linewidth}{cX}
        \textbf{d5}  & \textbf{Spell Scroll} \\
        1 & Witch Bolt \\
        2 & Disguise Self \\
        3 & Thunderwave \\
        4 & Expeditious Retreat \\
        5 & Protection from good \& evil \\
      \end{tabularx}
    \end{tabularz}

  \section{Random Tables}
    Choose your own adventure, but with dice.

    \subsection{Wild Magic}
    When Sorcerer's cast a non-cantrip spell, they must roll to determine if any wild magic occurs.
    \begin{tabularz}
      \begin{tabularx}{\linewidth}{cX}
        \textbf{d8}  & \textbf{Magic Surge} \\
        1 & Unicorn appears within 5 feet for the next minute \\
        2 & One of the targets' eyes are replaced by a 500 GP sapphire \\
        3 & Cannot speak, emit pink bubbles instead \\
        4 & Caster can only speak to animals for 24 hours \\
        5 & Surrounded by faint ethereal music for 1 minute \\
        6 & Caster grows antlers, but sheds them in 24 hours \\
        7 & Caster and the target switch positions after spell \\
        8 & Glow brightly for 1 minute. Blind others within 5 feet \\
      \end{tabularx}
    \end{tabularz}

  \end{cols}
\end{document}

